---
title: "120 N Franklin Fruit Snack Apocalypse"
output:
  html_document:
    number_sections: true
    code_folding: hide
    theme: sandstone
    highlight: tango
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lme4)
library(rstanarm)
library(emmeans)
library(DT)
library(ggalluvial)
library(broom.mixed)

options(contrasts = rep("contr.sum", 2))

theme_set(theme_dark(14))
```

# Data

Everybody's ratings are in the table below, click on your name to sort your ratings from highest-to-lowest, or from lowest-to-highest.

```{r}
ratings <- read_csv(
  here::here("data/ratings.csv"),
  col_types = "iiiiiiiiiiiiic"
) %>% 
  select(fruit_snack_type, brand, consumption_order, everything())

datatable(ratings, rownames = FALSE, filter = "none", options = list(pageLength = 8, scrollX = TRUE))
```

# Visualization of the data

Here's all of the ratings at all at once. Note that Jon did not rate the Funables Mixed Berry flavor. Shame!

```{r}
tasters <- c(
  "kath",
  "kate",
  "gaby",
  "jon",
  "emily",
  "will",
  "rage",
  "mickey",
  "chris",
  "christian",
  "alex",
  "lauren"
)

ratings_long <- ratings %>%
  mutate_at(vars(fruit_snack_type), fct_inorder) %>%
  pivot_longer(
    cols = one_of(tasters),
    names_to = "rater",
    values_to = "rating"
  )

ratings_long %>%
  ggplot(aes(rater, fct_rev(fruit_snack_type), fill = rating)) +
  geom_tile() +
  scale_fill_distiller(direction = 1, limits = c(1, 5), palette = "RdYlGn") +
  theme(
    axis.title = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    fill = "rating",
    caption = "Rows in order of consumption, beginning with Annie's Sunny Citrus"
  )
```

# Average ratings by fruit snack

The average fruit snack ratings look like this. Welch's Mixed Fruit was the most popular and Betty Crocker Trolls was the least popular.

```{r}
ols <- lm(rating ~ fruit_snack_type + rater, data = ratings_long)

fit <- lme4::lmer(rating ~ fruit_snack_type + (1 | rater), data = ratings_long)
# summary(fit)

fit_emm <- emmeans(fit, ~fruit_snack_type, lmer.df = "satterthwaite")

broom::tidy(fit_emm, conf.int = TRUE) %>%
  arrange(estimate) %>%
  mutate_at(vars(fruit_snack_type), fct_inorder) %>%
  ggplot(aes(x = fruit_snack_type, y = estimate, ymin = conf.low, ymax = conf.high, color = estimate)) +
  geom_pointrange() +
  scale_color_distiller(direction = 1, limits = c(1, 5), palette = "RdYlGn") +
  coord_flip() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "none"
  ) +
  labs(
    title = "Fruit snack ratings by snack",
    y = "Estimated rating"
  )
```

# Average ratings by rater

The average fruit snack ratings look like this. Welch's Mixed Fruit was the most popular and Betty Crocker Trolls was the least popular.

```{r}
# coef(fit)$rater %>% 
#   janitor::clean_names() %>% 
#   select(intercept)

fixed_intercept <- 2.2846  # from fit

tidy(fit, effects = "ran_vals", conf.int = TRUE) %>% 
  arrange(desc(estimate)) %>% 
  mutate(
    rater = fct_rev(fct_inorder(level))
  ) %>% 
  ggplot() +
  aes(
    x = rater, 
    y = estimate + fixed_intercept,
    ymin = conf.low + fixed_intercept,
    ymax = conf.high + fixed_intercept,
    color = estimate + fixed_intercept
  ) +
  geom_pointrange() +
  scale_color_distiller(direction = 1, limits = c(1, 5), palette = "RdYlGn") +
  coord_flip() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "none"
  ) +
  labs(
    title = "Average rating by rater",
    y = "Estimated rating"
  )
```

# Did we get sick of fruit snacks over time?

I was curious if we all got sick of fruit snacks over the course of the evening and our ratings went down as a result. It looks like this might have been the case for some people but not for everyone.

```{r}
ratings_long %>% 
  na.omit() %>% 
  ggplot() +
  aes(x = consumption_order, y = rating) +
  geom_smooth(se = FALSE, method = "lm", linetype = "dashed", formula = y ~ x, color = "darkgrey") +
  geom_line() +
  geom_point(aes(color = rating)) +
  scale_color_distiller(direction = 1, limits = c(1, 5), palette = "RdYlGn") +
  facet_wrap(vars(rater)) +
  labs(
    y = "Rating",
    x = "Number of fruit snacks consumed so far",
    caption = "Dashed lines from simple linear regression"
  )
```

# Ratings by rater and brand

```{r}
ratings_long %>%
  mutate(
    brand = as.factor(brand)
  ) %>% 
  group_by(brand, rater) %>% 
  mutate(average_rating = mean(rating)) %>% 
  ggplot(aes(rater, fct_rev(brand), fill = average_rating)) +
  geom_tile() +
  scale_fill_distiller(direction = 1, limits = c(1, 5), palette = "RdYlGn") +
  theme(
    axis.title = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    fill = "rating",
    title = "Average ratings by rater and brand"
  )
```

